---
title: "TRO Outfalls v0.3"
style: center
author: "Steve Hummel DEQ Tidewater" 
output: 
  flexdashboard::flex_dashboard:
      navbar:
      - { icon: "fa-question-circle", href: "https://hangouts.google.com/?action=chat&pi=115347244789652424079", align: right }
self_contained: true
source_code: embed
---
<style>                     
.navbar {
  background-color:black;
  border-color:deepskyblue;
  font-family: Georgia; 
  font-size: 20px; 
  font-style: normal; 
  font-variant: normal;
  font-weight: 700; 
  line-height: 26.4px;
  text-align: center

}
.navbar-brand {
color:deepskyblue!important;
border-color:black
}
.navbar-author {
color:#424949;
font-size: 11px
}
.first-box {
background-color: black;
color: 		deepskyblue;
border-color:black
}
.second-box {
background-color: #424949;
color: 	deepskyblue;
border-color:#424949
}
.first-col {
background-color: black;
color: 	deepskyblue;
border-color:black
}
.datatable {
background-color: #424949;
color: 	white;
border-color:black
}
</style>  

```{r results='hide', message=FALSE, warning=FALSE}

library(leaflet)
library(crosstalk)
library(tidyverse)
#library(FedData)
library(magrittr)
library(GISTools)
#library(gdistance)
#library(ggmap)
library(sp)
library(rgeos)
library(sp)
library(rgdal)
library(mapview)
library(sf)
library(leafem)
library(shiny)
library(raster)
library(DT)
library(shinyjs)
library(dplyr)
#library(spdplyr)
library(htmlTable)
library(htmltools)
library(rhandsontable)
library(inlmisc)
library(nhdR)
library(leaflet.extras)

WGS84 <-CRS("+proj=longlat +datum=WGS84") 
#WGS84 <-CRS("+proj=utm +zone=18 +init=epsg:32147") 

####### sHAPE fILES########################

dir="C:/Users/vvt97279/Documents/outfalls"
Files=list.files(dir,pattern="shp$", full.names = TRUE)

x <- lapply(Files, shapefile)

y=lapply(x,spTransform,CRS("+proj=longlat +datum=WGS84"))

names(y)=gsub("C:/Users/vvt97279/Documents/outfalls/","",Files)


#Remove all shapes other than impairments
y2=y[-c(3,17,18)]


final15=read.csv("New_all_combined2.csv",h=T)

final=read.csv("New_all_combined2.csv",h=T)

#New_All500 %>% filter(distance < 500) %>% mutate(distance=round(distance,2))

final15=final15 %>% filter(distance < 500) %>% mutate(distance=round(distance,0))

final15_sf <- st_as_sf(final15, crs = 4326, coords = c("LON", "LAT"))
Huc_tro=st_transform(st_read("C:/Users/vvt97279/Documents/outfalls/TidewaterHUC6.shp"),crs=4326)
Huc_join=st_join(final15_sf,Huc_tro,join=st_within)
st_geometry(Huc_join) <- NULL

#final_sf <- st_as_sf(final, crs = 4326, coords = c("LON", "LAT"))
#Huc_join_final=st_join(final_sf,Huc_tro,join=st_within)
#st_geometry(Huc_join_final) <- NULL

Huc_join$LAT=final15$LAT
Huc_join$LON=final15$LON


blue=Huc_join[,c("Permit.Number","Outfall.No","LON","LAT","Total_Outfalls",
            "distance","Local_TMDL","Within_ChesBay","WLA","Receiving.Stream","ID305B","Type","Facility","Outfalls_same_Loc","POL_NAME","IMP_NAME","PJ_NAME","VAHU6","HUC12")]


red=final15[,c("Permit.Number","Outfall.No","lon","lat","Total_Outfalls",
            "distance","Local_TMDL","Within_ChesBay","WLA","Receiving.Stream","ID305B","Type","Facility","Outfalls_same_Loc","POL_NAME","IMP_NAME","PJ_NAME")]




shared <- SharedData$new(blue,group="subset")


```

Column 1 { .first-box}
--------------------------------------------------


### Filter outfalls by manipulating parameters {.first-box data-height=200}

```{r}

pal1 <- colorFactor(palette = c("blue", "red", "green","orange"), 
                   levels = c("DO", "Bacteria", "Benthic","pcb"))

pal2 <- colorFactor(palette = c("green", "red", "red","red"), 
                    levels = c("Benthic-Macroinvertebrate Bioassessments (Streams)", "Total Fecal Coliform", "Escherichia coli","Enterococcus"))

listpal = c("DO", "Bacteria", "Benthic","pcb")

#Bact
y$Bacteria.shp@data$Type="Bacteria"
y$Estuarine_Bact.shp@data$Type="Bacteria"
#DO
y$Reservoir_DO.shp@data$Type="DO"
y$DO.shp@data$Type="DO"
y$Estaurine_DO.shp@data$Type="DO"
#Benthic
y$Estaurine_Benthic.shp@data$Type="Benthic"
y$Benthic.shp@data$Type="Benthic"

#pcb
y$Estaurine_pcb.shp@data$Type="pcb"
y$Reservoir_pcb.shp@data$Type="pcb"



 m=filter_checkbox("chesbay", "ChesBay", shared, ~Within_ChesBay, inline = T)
 m2=filter_select("sites", "Permit.Number", shared, ~Permit.Number)
m500=filter_select("huc", "VAHU6", shared, ~VAHU6)
 m3=filter_select("fac", "Facility", shared, ~Facility)
 mm= filter_checkbox("tmdl", "TMDL", shared, ~Local_TMDL, inline = T)
 mmm=filter_slider("hp", "distance (meters)", shared, ~round(distance,1), width = "80%",step=1)


box=bbox(y$Tidewater.shp)


bscols(
list(m2,m3),
list(mm,m),
m500
)
 
#sd_dt3=SharedData$new(final500[ ,c("Facility","Outfall.No")], group = "subset")
#d=datatable(sd_dt3, rownames=FALSE, options=list(dom='tp'), width=50)
#d
```

### Outfalls 500 meters or less from impaired waters{ .second-box }

```{r}

opt <- leaflet::markerClusterOptions(showCoverageOnHover = FALSE)
  
   b=CreateWebMap()%>%
  leaflet::setView(lng = -76.4, lat = 37, zoom = 09) %>%
  #  leaflet::addProviderTiles("Esri.WorldImagery", group="Imagery") %>%
 #     leaflet::addTiles(attribution = NULL,options = providerTileOptions(noWrap = TRUE), #group="Street") %>%
          #leaflet::addTiles(urlTemplate = "", attribution = NULL)%>%
           #setView(lng = -78.39844, lat = 37.82715, zoom=8) %>%
           mapview::addMouseCoordinates(style = "basic") %>%
           addPolygons(fill = FALSE,data=y$Tidewater.shp,group="TRO",color="yellow") %>%
           addPolygons(fill = TRUE,data=y$TMDL.shp,group="TMDL",label=~POL_NAME,popup=~paste0(PJ_NAME,"<br>","<a href='",y$TMDL.shp$PJ_RPT_FIN,"'>","Link to TMDL","</a>"),color=~pal2(IMP_NAME))%>%
           addPolygons(fill = FALSE,data=y$Reservoir_DO.shp,group="DO",color="blue") %>%
           addPolygons(fill = TRUE,data=y$Estuarine_Bact.shp,group="Bacteria",color="red") %>%
           addPolygons(fill = TRUE,data=y$Estaurine_Benthic.shp,group="Benthic",color="green") %>%
           addPolygons(fill = TRUE,data=y$Estaurine_pcb.shp,group="PCB",color="orange",popup= ~WATER_NAME,label=~ID305B) %>%
           addPolygons(fill = TRUE,data=y$Reservoir_pcb.shp,group="PCB",color="orange",popup= ~WATER_NAME,label=~ID305B) %>%
           #addPolygons(fill = FALSE,data=CB,group="ChesBay") %>%
           addPolylines(data=y$Bacteria.shp,group="Bacteria",color= ~pal1(Type),popup= ~WATER_NAME,label=~ID305B) %>%
           addPolylines(data=y$Benthic.shp,group="Benthic",color=~pal1(Type),popup= ~WATER_NAME,label=~ID305B) %>%
           addPolylines(data=y$DO.shp,group="DO",color= ~pal1(Type),popup= ~WATER_NAME,label=~ID305B) %>% 

#addCircleMarkers(data=blue,radius=5,fillOpacity = 0.5, weight = 2, fillColor = "white",group="All_Outfalls") %>%
             
addCircleMarkers(
data=shared,radius=6,color="#7FFF00",fillOpacity=0.9,fillColor="blue",weight=2,group="Outfalls",lng=~LON,lat=~LAT,label=~Facility,popup = paste("Ourfall_Number",final15$Outfall.No,"<br>","Permit:",final15$Permit.Number,"<br>","Meters to nearest impaired:","<b>",round(final15$distance,2),"</b>","<br>","Rec Water:",final15$Receiving.Stream,"<br>","Nearest impaired:",final15$Type,"<br><b>","Impaired Reach Location","</b>","<br>",final15$LOCATION,"<br>","<br>","Nearest 305(b) ID",final15$ID305B,
                                                                                                                                          "<br>","VAHUC6",blue$VAHU6,"<br>","HUC12",blue$HUC12))%>%

addCircleMarkers(clusterOptions = opt, clusterId = "cluster",
data=shared,radius=6,color="#7FFF00",fillOpacity=0.9,fillColor="black",weight=2,group="clusters",lng=~LON,lat=~LAT,label=~Facility,popup = paste("Ourfall_Number",final15$Outfall.No,"<br>","Permit:",final15$Permit.Number,"<br>","Meters to nearest impaired:","<b>",round(final15$distance,2),"</b>","<br>","Rec Water:",final15$Receiving.Stream,"<br>","Nearest impaired:",final15$Type,"<br><b>","Impaired Reach Location","</b>","<br>",final15$LOCATION,"<br>","<br>","Nearest 305(b) ID",final15$ID305B,
                                                                                                                                                 "<br>","VAHUC6",blue$VAHU6,"<br>","HUC12",blue$HUC12))%>%     
     
addCircleMarkers(color="red",fillColor="red",data=red,weight=1.5,radius=4,group="snapped Outfalls",lng=~lon,lat=~lat,label=~Facility,popup = paste("Facility",final15$Facility,"<br>","meters",round(final15$distance,2),"<br>",final15$Type,"<br>",final15$WATER_NAME))

 

b=leaflet::addLayersControl(b,overlayGroups=c("TMDL","TRO","Bacteria","Benthic","DO","PCB","snapped Outfalls","Outfalls","clusters"),
  baseGroups = c("Topo","Imagery","Hydrography"),
  options = layersControlOptions(collapsed = TRUE)) 
  
  
b=leaflet::addLegend(b,pal = pal1,values = listpal, 
                              position = "topright", 
                              title = "Impairment") 
  
b=addMeasure(b,position = "topleft", primaryLengthUnit = "meters") 
  
b=leaflet::showGroup(b,"Outfalls")
b=leaflet::hideGroup(b,c("TMDL","TRO","DO","Benthic","Bacteria","PCB","snapped Outfalls","clusters"))
b=leaflet.extras::addFullscreenControl(b,position = "bottomright")

b=inlmisc::AddHomeButton(b,extent(box),position = "topleft")  

b=inlmisc::AddSearchButton(b, group = "Outfalls", zoom = 15,
                           textPlaceholder = "Search facility names...")

b=inlmisc::AddClusterButton(b, clusterId = "cluster")

b

```

Column 2 { .first-box}
--------------------------------------------------

### slider{.first-box data-height=80}

```{r}
mmm
```


### Table {.datatable}
```{r}

sd_dt=SharedData$new(final15[,c("Facility","Permit.Number","Outfall.No","Total_Outfalls",
            "distance","Local_TMDL","Within_ChesBay","WLA","Receiving.Stream","ID305B","Type","Outfalls_same_Loc","LON","LAT","POL_NAME","IMP_NAME","PJ_NAME")], group = "subset")

datatable(sd_dt, rownames = FALSE,
  extensions = 'Buttons',style="bootstrap",
  class="compact", width="100%",
  options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'
      ))
    
  )
)

```

