---
title: "BRO Outfalls v0.0"
style: center
author: "Steve Hummel DEQ Tidewater" 
output: 
  flexdashboard::flex_dashboard:
      navbar:
      - { icon: "fa-question-circle", href: "https://hangouts.google.com/?action=chat&pi=115347244789652424079", align: right }
self_contained: true
source_code: embed
---
<style>                     
.navbar {
  background-color:black;
  border-color:#EC7063;
  font-family: Lucida Grande; 
  font-size: 20px; 
  font-style: normal; 
  font-variant: normal;
  font-weight: 700; 
  line-height: 26.4px;
  text-align: center

}
.navbar-brand {
color:#EC7063!important;
border-color:black
}
.navbar-author {
color:#424949;
font-size: 11px
}
.first-box {
background-color: black;
color: 		#EC7063;
border-color:black;

}
.second-box {
background-color: #424949;
color: 	#EC7063;
border-color:#424949
}
.first-col {
background-color: black;
color: 	#EC7063;
border-color:black
}
.datatable {
background-color: #424949;
color: 	white;
border-color:black
}
{
.irs-bar,
.irs-bar-edge,
.irs-single,
.irs-grid-pol {
  background: red;
  border-color: red;
}
</style>  

```{r results='hide', message=FALSE, warning=FALSE}

library(leaflet)
library(crosstalk)
library(tidyverse)
#library(FedData)
library(magrittr)
library(GISTools)
#library(gdistance)
#library(ggmap)
library(sp)
library(rgeos)
library(sp)
library(rgdal)
library(mapview)
library(sf)
library(leafem)
library(shiny)
library(raster)
library(DT)
library(shinyjs)
library(dplyr)
#library(spdplyr)
library(htmlTable)
library(htmltools)
library(rhandsontable)
library(inlmisc)
library(nhdR)
library(leaflet.extras)

prj <- CRS("+proj=utm +zone=18 +datum=WGS84 +units=ft")
WGS84 <-CRS("+proj=longlat +datum=WGS84")

dir="C:/Users/vvt97279/Documents/outfalls/BRO"

Files2=list.files(dir,pattern="shp$", full.names = T)
Files2=Files2[c(-1,-8)]


shapes=lapply(Files2,readOGR) 
shapes2=lapply(shapes,spTransform,CRS("+proj=longlat +datum=WGS84")) 

shapes3=shapes2[c(-7,-8)]

names(shapes3)=(c("reservoirbacteria","reservoirchla",
            "reservoirDO","reservoirHg",
            "reservoirpcb","reservoirpH","riverinebacteria","riverinebenthics",
            "riverineDO","riverineHg","riverinepcb","riverinepH","riverinetemp"))




TMDL=readOGR(dsn="~/outfalls",layer="TMDL")
TMDL=spTransform(TMDL, WGS84)

BRO=readOGR(dsn="~/outfalls/BRO",layer="BRO")
BRO=spTransform(BRO, WGS84)


inside=raster::intersect(TMDL, BRO)


bro_data=read.csv("Imp_Out_TMDL.csv",h=T) %>%
filter(distance.to.impaired < 500) %>%
group_by(Facility) %>% arrange(distance.to.impaired)




#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


shared <- SharedData$new(bro_data,group="subset")
shared2 <- SharedData$new(bro_data,group="subset")


```

Column 1 { .first-box}
--------------------------------------------------


### Filter outfalls by manipulating parameters {.first-box data-height=200}

```{r}

pal1 <- colorFactor(palette = c("red", "green", "blue","brown","purple","cyan",
                                "yellow","black"), 
                   levels = c("bacteria", 
                              "chla", "DO",
                              " Hg","pcb","pH",
                            "benthics","temp"))

pal2 <- colorFactor(palette = c("green", "red", "red","red"), 
                    levels = c("Benthic-Macroinvertebrate Bioassessments (Streams)", "Total Fecal Coliform", "Escherichia coli","Enterococcus"))

listpal = c("DO", "bacteria", "benthics","pcb","pH","temp","Hg","chla")



 m=filter_checkbox("tmdlimp", "Staff", shared, ~Permit.Writer, inline = T)
 m2=filter_select("sites", "Permit.Number", shared, ~Permit.Number)
 m3=filter_select("fac", "Facility", shared, ~Facility)
 mm= filter_checkbox("tmdl", "TMDL", shared, ~Local_TMDL, inline = T)
 mmm=filter_slider("hp", "distance (meters)", shared, ~round(distance.to.impaired,1), width = "80%",step=1)


box=bbox(BRO)


bscols(
list(m2,m3),
list(mm,m)
)
 



#sd_dt3=SharedData$new(final500[ ,c("Facility","Outfall.No")], group = "subset")
#d=datatable(sd_dt3, rownames=FALSE, options=list(dom='tp'), width=50)
#d
```

### Outfalls 500 meters or less from impaired waters{ .second-box }

```{r}

s=data.frame(unique(bro_data$ASSESSMENT))

opt <- leaflet::markerClusterOptions(showCoverageOnHover = FALSE)
  
  b=CreateWebMap()%>%
  leaflet::setView(lng = -79.72881, lat =37.25088, zoom = 09) %>%
  #  leaflet::addProviderTiles("Esri.WorldImagery", group="Imagery") %>%
 #     leaflet::addTiles(attribution = NULL,options = providerTileOptions(noWrap = TRUE), #group="Street") %>%
          #leaflet::addTiles(urlTemplate = "", attribution = NULL)%>%
           #setView(lng = -78.39844, lat = 37.82715, zoom=8) %>%
    #       mapview::addMouseCoordinates(style = "basic") %>%
           addPolygons(fill = FALSE,data=BRO,group="BRO",color="black") %>%
           addPolygons(fill = TRUE,data=inside,group="TMDL",label=~POL_NAME,popup=~paste0(PJ_NAME,"<br>","<a href='",inside$PJ_RPT_FIN,"'>","Link to TMDL","</a>"),color="grey")%>%
           
    addPolygons(fill = FALSE,
                data=shapes3[[1]],group="Bacteria",popup=popupTable(shapes3[[1]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="red") %>%
    addPolylines(fill = F,data=shapes3[[7]],group="Bacteria",popup=popupTable(shapes3[[7]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="red") %>%
    addPolygons(fill = T,data=shapes3[[2]],group="chla",popup=popupTable(shapes3[[2]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="green") %>%                  
    addPolygons(fill = T,data=shapes3[[3]],group="DO",popup=popupTable(shapes3[[3]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="blue") %>%  
    addPolygons(fill = T,data=shapes3[[4]],group="Hg",popup=popupTable(shapes3[[4]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="brown") %>%  
    addPolygons(fill = T,data=shapes3[[5]],group="pcb",popup=popupTable(shapes3[[5]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="purple") %>%  
    addPolygons(fill = T,data=shapes3[[6]],group="pH",popup=popupTable(shapes3[[6]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="cyan") %>%  
    addPolylines(fill = FALSE,data=shapes3[[8]],group="Benthic",popup=popupTable(shapes3[[8]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="yellow") %>%  
    addPolylines(fill = FALSE,data=shapes3[[9]],group="DO",popup=popupTable(shapes3[[9]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="blue") %>%  
     addPolylines(fill = FALSE,data=shapes3[[13]],group="temp",popup=popupTable(shapes3[[13]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="blue") %>%
      addPolylines(fill = FALSE,data=shapes3[[10]],group="Hg",popup=popupTable(shapes3[[10]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="brown") %>%
      addPolylines(fill = FALSE,data=shapes3[[11]],group="pcb",popup=popupTable(shapes3[[11]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="purple") %>%
          addPolylines(fill = FALSE,data=shapes3[[12]],group="pH",popup=popupTable(shapes3[[12]],zcol = c("WATER_NAME","IMP_CAUSE",                                                                                         "CATEGORY")),label=~WATER_NAME,color="cyan") %>%

  leaflet::addLayersControl(overlayGroups=c("TMDL","BRO","Bacteria","Benthic","DO","pcb","pH","chla","Hg","temp","snapped Outfalls","Outfalls","clusters"),
  baseGroups = c("Topo","Imagery","Hydrography"),
  options = layersControlOptions(collapsed = TRUE)) %>%
  
  
leaflet::addLegend(pal = pal1,values = listpal, 
                              position = "topright", 
                              title = "Impairment") %>%
  
addCircleMarkers(
data=shared,radius=6,color="#7FFF00",fillOpacity=0.9,fillColor="blue",weight=2,group="Outfalls",lng=~Longitude.Decimal,lat=~Latitude.Decimal,label=~Facility,popup = paste("<b>",bro_data$Facility,"</b><br>","Ourfall_Number",bro_data$Outfall.No,"<br>","Permit:",bro_data$Permit.Number,"<br>","Meters","<b>",round(bro_data$distance.to.impaired,0),"</b>","<br>","RecWater:",bro_data$Receiving.Stream.x,"<br><b>","Impaired Water:",bro_data$WATER_NAME,"</b><br>","Impairment Loc:","</b>","<br>",bro_data$LOCATION,"<br>","<br>","All Impairments for","<b>",bro_data$ID305B,"</b><br>",bro_data$IMP_CAUSE,"<br>","TMDL Name:",bro_data$PJ_NAME,"<br>","<a href='",bro_data$PJ_RPT_FIN,"'>","Link to TMDL","</a>"))%>%

addCircleMarkers(
data=bro_data,color="red",fillColor="red",weight=1.5,radius=4,group="snapped Outfalls",lng=~lon,lat=~lat,
label=~Facility,popup = paste("Facility",bro_data$Facility,"<br>","Ourfall_Number",bro_data$Outfall.No,"<br>","Permit:",bro_data$Permit.Number,"<br>","Meters","<b>",round(bro_data$distance.to.impaired,2),"</b>","<br>","Rec Water:",bro_data$Receiving.Stream.x,"<br>"," Impairment:",bro_data$ASSESSMENT,"<br><b>","Permit Writer","</b>","<br>",bro_data$Permit.Writer,"<br>","<br>","Nearest 305(b) ID",bro_data$ID305B,"<br>",bro_data$WATER_NAME)) 
    
   


b=addMeasure(b,position = "topleft", primaryLengthUnit = "meters") 
  
b=leaflet::showGroup(b,"Outfalls")
b=leaflet::hideGroup(b,c("TMDL","BRO","Bacteria","Benthic","DO","pcb","pH","chla","Hg","temp","snapped Outfalls"))
b=leaflet.extras::addFullscreenControl(b,position = "bottomright")

b=inlmisc::AddHomeButton(b,extent(box),position = "topleft")  

b=inlmisc::AddSearchButton(b, group = "Outfalls", zoom = 15,
                           textPlaceholder = "Search facility names...")

b=inlmisc::AddClusterButton(b, clusterId = "cluster")

b

```

Column 2 { .first-box}
--------------------------------------------------

### slider{.first-box data-height=80}

```{r}
mmm
```


### Table {.datatable}
```{r}
brchop=bro_data

sd_dt=SharedData$new(brchop,group="subset")

datatable(sd_dt, rownames = FALSE,
  extensions = 'Buttons',style="bootstrap",
  class="compact", width="100%",
  options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download' )))) %>% formatStyle("LOCATION","white-space"="nowrap")



```

